Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Sampling Approach taken in Pollster
Sampling Approach taken in Pollster

>>>>

The Marquette Law School Poll combines ABS and stratified random sampling. The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach. To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses. Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups. This probability-based sampling minimizes bias but requires significant resources. Stratification and weighting to represent specific populations add to survey complexity and cost.
